Workshop Demo Doc

### 2019-05-19 demo-doc.Rmd
update typos/edits based on presentation

```{r}
gss_cat %>% 
  select(year, marital, tvhours)
```

@@

```{r}
gss_cat %>% 
  filter(age > 30)
```

@@

```{r}
gss_cat %>% 
  mutate(potential_senior = if_else(age >= 60, TRUE, FALSE))
```

@@

```{r}
gss_cat <- gss_cat %>% 
  mutate(potential_senior = if_else(age >= 60, TRUE, FALSE))
```

@@

```{r}
m1 <- lm(tvhours ~ age, summary = gss_ct)
summary(m1)
```

@@

```{r}
m2 <- lm(tvhours ~ age + , summary = gss_ct)
summary(m1)
```

>>>>

```{r}
gss_cat %>% 
  select(year, tvhours)

gss_cat %>% 
  select(year, marital, tvhours)
```

@@

```{r}
gss_cat %>% 
  filter(age > 60)
```

@@

```{r}
gss_cat %>% 
  mutate(potential_senior = if_else(age >= 63.5, 1, 0),
         super_senior = if_else(potential_senior == 1 & tvhours < 2, 1, 0)) %>% 
  count(potential_senior, super_senior)
```

@@

```{r}
gss_cat <- gss_cat %>% 
  mutate(potential_senior = ifelse(age >= 63.5, TRUE, FALSE))
```

Adding another variable for folks who are middle-aged.

```{r}
gss_cat <- gss_cat %>% 
  mutate(middle_aged = ifelse(age >= 30 & age <= 40, "yes", "no"))
```

@@

```{r}
m1 <- lm(tvhours ~ age, data = gss_cat)
summary(m1)
```

@@

```{r}
m2 <- lm(tvhours ~ age + , data = gss_cat)
summary(m1)
```
